Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-10-21 robdml.tex
tex

%%%%%%%%% ABSTRACT
\begin{abstract}
	% background
	Owing to the significance of the adversarial vulnerability of deep metric
	learning models, which poses safety and security implications in its
	applications, a series of defense methods have been proposed to improve its
	adversarial robustness.
	% insight
	In order to avoid model collapse due to excessively hard examples, the
	existing methods refrain from using the typical min-max adversarial
	training paradigm, but instead learn from a weak adversary.
	% our starting point
	However, we argue that a model can learn from a strong adversary without
	model collapse, where the key for overall performance is triplet hardness.
	% HM framework
	To this end, Hardness Manipulation is proposed to adversarially perturb
	the training triplet to increase its hardness into a specified level,
	by referencing other benign triplets, or a pseudo-hardness function.
	% GA Adversary
	To further improve the model performance, we propose a Gradual Adversary to
	dynamicly change the hardness level to balance metric learning and
	adversarial learning.
	% Experiment
	The proposed method is validated on three commonly used deep metric
	learning datasets, namely CUB-200-2011, Cars-196, and Stanford Online
	Product.
	% Conclusion
	Comprehensive experimental results show our method outperforms the existing
	defense methods, while achieving clearly higher efficiency at a lower
	training cost.  
%
\end{abstract}

>>>>

%%%%%%%%% ABSTRACT
\begin{abstract}
	% background
	Owing to the significance of the adversarial vulnerability of deep metric
	learning models, which poses safety and security implications in its
	applications, a series of defense methods have been proposed to improve its
	adversarial robustness.
	% insight
	In order to avoid model collapse due to excessively hard examples, the
	existing methods refrain from using the typical min-max adversarial
	training paradigm, but instead learn from a weak adversary.
	% our starting point
	Conversely, we argue that a model can learn from a strong adversary without
	collapse, where the key is triplet hardness.
	% HM framework
	To this end, Hardness Manipulation is proposed to adversarially perturb the
	training triplet to increase its hardness into a specified level, by
	referencing other benign triplets, or a pseudo-hardness function.
	% GA Adversary
	Based on this, Gradual Adversary is proposed as a family of pseudo-hardness
	functions to overcome problems of referencing other benign triplets, and
	achieve a better balance in the learning objective.
	% ICS
	\oo{ICS}
	% Experiment and Conclusion
	Comprehensive experimental results on three commonly used deep metric
	learning datasets suggest that the proposed method, albeit remains
	simple, overwhelmingly outperforms the state-of-the-art defense
	methods in terms of robustness, training cost, as well as recall
	performance on benign examples.
%
\end{abstract}
